---
title: "Assignment 1"
author: "Wenhao Li 250959325"
date: "26/01/2020"
output:
  pdf_document: default
  word_document: default
---

# Question 1
```{r}
#Find all possible R built-in functions related to exp distribution 
search()
objects(3)
```
The R bulit-in functions related to exp distribution are dexp, pexp, qexp and rexp.
Rexp generates random deviates.
Dexp gives the density.

```{r}
curve(dexp,from=0,to=4)
```

The code curve(dexp,from=0,to=4) plots Exp(1)'s distibution, where x is from 0 to 4 (domain of x is[0,4]).








# Question 2
```{r}
# Use for loop for sum
sum1<-0
for (i in 1:100) {
  sum1<-sum1+i
}
sum1
# Use for R function for sum
sum(1:100)
sum1==sum(1:100)


# Use for loop for mean
sum1_mean<-0
for (i in 1:100) {
  sum1_mean<-sum1_mean*(i-1)/i+1
}
sum1_mean
# Use for R function for mean
mean(1:100)
sum1_mean==mean(1:100)
```
When we use R function and for loop to get the sum and mean, we can get the same result. However, using R function directly is better. Because it has less steps and it is more convenience to be read.








# Question 3
```{r}
# n=10;Use for loop and compare with geometric series formula
n_10<-0
for (j in 0:10) {
  n_10<- n_10+1.08^j
}
n_10
n_10_formula<-(1-1.08^11)/(1-1.08)
n_10_formula
n_10==n_10_formula

#n=20;Use for loop and compare with geometric series formula
n_20<-0
for (j in 0:20) {
  n_20<- n_20+1.08^j
}
n_20
n_20_formula<-(1-1.08^21)/(1-1.08)
n_20_formula
n_20==n_20_formula

#n=30;Use for loop and compare with geometric series formula
n_30<-0
for (j in 0:30) {
  n_30<- n_30+1.08^j
}
n_30
n_30_formula<-(1-1.08^31)/(1-1.08)
n_30_formula
n_30==n_30_formula

#n=40;Use for loop and compare with geometric series formula
n_40<-0
for (j in 0:40) {
  n_40<- n_40+1.08^j
}
n_40
n_40_formula<-(1-1.08^41)/(1-1.08)
n_40_formula
n_40==n_40_formula


#n=10;Use sum function and compare with geometric series formula
sum_n10<-0
sum_n10<-sum(1.08^(0:10))
sum_n10
n_10_formula
sum_n10==n_10_formula

#n=20;Use sum function and compare with geometric series formula
sum_n20<-0
sum_n20<-sum(1.08^(0:20))
sum_n20
n_20_formula
sum_n20==n_20_formula

#n=30;Use sum function and compare with geometric series formula
sum_n30<-0
sum_n30<-sum(1.08^(0:30))
sum_n30
n_30_formula
sum_n30==n_30_formula

#n=40;Use sum function and compare with geometric series formula
sum_n40<-0
sum_n40<-sum(1.08^(0:40))
sum_n40
n_40_formula
sum_n40==n_40_formula

#Find difference when n=30
n_30-n_30_formula
n_30-sum_n30
c(sum_n30,n_30)
```
Using sum function and geometric series formula can give the same result.
When use for loop, it gives the same result with geometric series formula when n=10,20,40. When n=30, the result of for loop is different from the result of geometric series formula. However,when n=30, the difference between the result of for loop and the result of geometric series formula is small. The numerical rounding may leads to this difference.
Also, using sum function is better. It has less step and easier to be read.







# Question 4

Sample size 1000
```{r}
n<-1000
set.seed(721)
Sam1000<-numeric(15)
for (i in 1:15) {
  #Generate 1000 random numbers from Normal Distribution 
  sample1000<-rnorm(n,0,1)
  #Absolute values
  abs_sample1000<-abs(sample1000)
  #The absolute values that is less than 2
  small_abs_sample1000<-abs_sample1000<2
  #The proportion
  Sam1000[i]<-mean(small_abs_sample1000)
}
Sam1000
```

Sample size 10000
```{r}
n<-10000
set.seed(721)
Sam10000<-numeric(15)
for (i in 1:15) {
  #Generate 10000 random numbers from Normal Distribution 
  sample10000<-rnorm(n,0,1)
  #Absolute values
  abs_sample10000<-abs(sample10000)
  #The absolute values that is less than 2
  small_abs_sample10000<-abs_sample10000<2
  #The proportion
  Sam10000[i]<-mean(small_abs_sample10000)
}
Sam10000
```

Comparation
```{r}
var(Sam1000)
max(Sam1000)-min(Sam1000)
var(Sam10000)
max(Sam10000)-min(Sam10000)
```
When sample size is 1000, the variance is 4.288571e-05, and the range is 0.024.
When sample size is 10000, the variance is 4.288571e-05, and the range is 0.0059.
The sample which size is larger(10000) has smaller variance and range.
As the sample size becomes larger,it will has smaller variance and range and the variation becomes smaller.
the variation of sample size 10000 does become smaller.






#Question 5
```{r}
col1<-seq(1:8)
col2<-rep(1:2,each=4)
col3<-rep(1:2,each=2,times=2)
col4<-rep(1:2,each=1,times=4)
Q5<-cbind(col1,col2,col3,col4)
matrix(Q5,nrow=8,ncol=4,byrow=FALSE)
```





#Question 6
```{r}
#Load build-in data frame cars 
data(cars)
```

#(a)
```{r}
help(cars)
```
There are 50 observations and 2 variables in the datasets. The name of variables are speed and dist.

#(b)
```{r}
#Find the observations that the car speed is 20 miles per hour
speed20<-cars[cars$speed==20,] 
#Get the mean of stopping distance of the car with 20 miles per hour speed 
mean(speed20$dist)
```
So the mean stopping distance for all observations for which the speed was 20 miles per hour is 50.4ft.

#(c)
```{r}
plot(x=cars$speed,y=cars$dist,main="Scatterplot of Stopping Distance VS Car Speed ",xlab="car speed",ylab="stopping distance")
```
There is a positive relationship between Stopping Distance and Speed. It is may be a linear positive relationship.







#Question 7
```{r}
#Load the built-in data frame USArrests
data("USArrests")
```

#(a)
```{r}
nrow(USArrests)
ncol(USArrests)
```
So there are 50 rows and 4 columns in this data frame.

#(b)
```{r}
#Calculate the median of each columb
median(USArrests$Murder)
median(USArrests$Assault)
median(USArrests$UrbanPop)
median(USArrests$Rape)
```
So the median of column Murder, Assault, UrbanPop and Rape are 7.25, 159, 66 and 30.1.

#(c)
```{r}
#Find the observations that the UrbanPop exceeds 77%
Urban_77<-USArrests$Murder[USArrests$UrbanPop>77]
#Get the average per capita murder rate
mean(Urban_77)
#Find the observations that the UrbanPop less than 50%
Urban_50<-USArrests$Murder[USArrests$UrbanPop<50]
#Get the average per capita murder rat
mean(Urban_50)
```
As a result, the avergae per capita murder rate (Murder) in regions where the percentage of the population living in urban areas (UrbanPop) exceeds 77% is 8.5.
The the avergae per capita murder rate (Murder) in regions where the percentage of the population living in urban areas (UrbanPop) less than 50% is 8.25.
The the avergae per capita murder rate (Murder) in regions where the percentage of the population living in urban areas (UrbanPop) less than 50% is smaller than the the avergae per capita murder rate (Murder) in regions where the percentage of the population living in urban areas (UrbanPop) less than 50%.

#(d)
```{r}
set.seed(721)
#A sample with sampling 12 rows from USArrests data frame withous replacement
Sam_12_row<-sample(1:50,12,replace = FALSE)
#Corrspond the rows
Sam_12<-USArrests[Sam_12_row,]
Sam_12
```

 

