---
title: "Assignment 5"
author: "Wenhao Li 250959325"
date: "30/03/2020"
output: word_document
---

# Question 1

# (a)
```{r}
fx<-function(x){
  cos(x)^2
  return(cos(x)^2)
}
curve(fx,from=0,to=2*pi)
```

# (b)
```{r}
set.seed(721)
n<-1000000
a<-runif(n,min=0,max=2*pi)
estimator<-mean(fx(a)/dunif(a,min=0,max=2*pi))
variance<-(mean((fx(a)/dunif(a,min=0,max=2*pi))^2)-estimator^2)/n
b<-sqrt(variance)
d<-estimator-1.96*b
e<-estimator+1.96*b
c(d,e)
estimator
```
Comment:
The area is 3.144901
The confidence interval is (3.140547,3.149255)

# (c)
```{r}
confidence.interval<-c(d,e)
pi<3.149255
3.140547<pi
```
Comment:
The exactly area is pi.
The confidence interval covers the true value.



# Question 2

# (a)
```{r}
set.seed(721)
x<-rnorm(100,10,2)
mean(x)
sd(x)
min(x)
max(x)
```
Comment:
Its mean is 9.784903.
The standard deviation is 2.299072.
The minimum value is 3.930008.
The maximum value is 13.98267.

# (b)
```{r}
set.seed(721)
booted.data<-replicate(50000,mean(sample(x,replace=TRUE)))
mean(booted.data)
sd(booted.data)
min(booted.data)
max(booted.data)
```
Comment:
Its mean is 9.784473.
The standard deviation is 0.2290073.
The minimum value is 8.69461.
The maximum value is 10.72199.

# (c)
```{r}
hist(booted.data,breaks=36,probability=TRUE)
```
The shape of this distribution is close to a normal distribution.
The center of this distribution is around 9.8.

# (d)
```{r}
theoretical.density<-function(x){
  dnorm(x,mean=0,sd=2/10)
}
hist(booted.data-mean(x),probability=TRUE,breaks=30)
curve(theoretical.density,add=TRUE,lty=2,col=2,from=-1,to=1)
```
Comment:
The shape is close to a normal distribution with center at 0.
The histogram of booted.data-mean(x) seems to fit the theoretical density (plot).

# (e)
```{r}
# Repeat first time
set.seed(720)
x<-rnorm(100,10,2)
mean(x)
sd(x)
min(x)
max(x)
set.seed(720)
booted.data<-replicate(50000,mean(sample(x,replace=TRUE)))
mean(booted.data)
sd(booted.data)
min(booted.data)
max(booted.data)
hist(booted.data,breaks=36,probability=TRUE)
theoretical.density<-function(x){
  dnorm(x,mean=0,sd=2/10)
}
hist(booted.data-mean(x),probability=TRUE,breaks=30)
curve(theoretical.density,add=TRUE,lty=2,col=2,from=-1,to=1)

# Repeat second time
set.seed(722)
x<-rnorm(100,10,2)
mean(x)
sd(x)
min(x)
max(x)
set.seed(722)
booted.data<-replicate(50000,mean(sample(x,replace=TRUE)))
mean(booted.data)
sd(booted.data)
min(booted.data)
max(booted.data)
hist(booted.data,breaks=36,probability=TRUE)
theoretical.density<-function(x){
  dnorm(x,mean=0,sd=2/10)
}
hist(booted.data-mean(x),probability=TRUE,breaks=30)
curve(theoretical.density,add=TRUE,lty=2,col=2,from=-1,to=1)
```
Comment:
The result changes a little. 
However, the shape of both new distributions are consistent with previous distribution.
They are all close to normal distribution (bell shape).



# Question 3

# (a)
```{r}
my.obj<-function(theta,x){
  a<-sum(abs(x-theta))
  return(a)
}
```

# (b)
```{r}
optimize.b<-function(x,interval=c(min(x),max(x))){
  b<-optimize(my.obj,x=x,interval=interval)
  return(b$minimum)
}
# Test 
optimize.b(c(3,7,9,12,15,18,21))
```

# (c)
```{r}
nlminb.c<-function(x,start=mean(x)){
  c<-nlminb(start,objective=my.obj,x=x)
  return(c$par)
}
# Test
nlminb.c(c(3,7,9,12,15,18,21))
```

# (d)
```{r}
k<-c(1,3,7,9,12,15,18,21)
optimize.b(k,interval=c(0,22))
optimize.b(k,interval=c(0,32))
optimize.b(k,interval=c(0,40))
nlminb.c(k,start=7)
nlminb.c(k,start=21)
nlminb.c(k,start=30)

d<-function(theta.d){
  sapply(theta.d,function(theta)my.obj(theta,k))
}
curve(d,from=min(k),to=max(k))
```
Comment:
With three different wider intervals, function from (b) has different results.
With three different start vaules,function from (c) has different results.
The graph fits the above values. 
When x is from 9 to 12, it has minimum value.



# Question 4

# (a)
```{r}
"huron" <- 
structure(.Data = c(581.55999999999995, 581.54999999999995, 581.34000000000003, 580.84000000000003, 
	580.33000000000004, 580.35000000000002, 579.87, 580.49000000000001, 
	579.90999999999997, 580.07000000000005, 580.90999999999997, 581.10000000000002,
	579.72000000000003, 580.32000000000005, 580.48000000000002, 580.38, 
	581.86000000000001, 580.97000000000003, 580.79999999999995, 579.78999999999996,
	580.38999999999999, 580.41999999999996, 580.82000000000005, 581.39999999999998,
	581.32000000000005, 581.44000000000005, 581.67999999999995, 581.16999999999996,
	580.52999999999997, 580.00999999999999, 579.90999999999997, 579.13999999999999,
	579.15999999999997, 579.54999999999995, 579.66999999999996, 578.44000000000005,
	578.24000000000001, 579.10000000000002, 579.09000000000003, 579.35000000000002,
	578.82000000000005, 579.32000000000005, 579.00999999999999, 579., 
	579.79999999999995, 579.83000000000004, 579.72000000000003, 579.88999999999999,
	580.00999999999999, 579.37, 578.69000000000005, 578.19000000000005, 
	578.66999999999996, 579.54999999999995, 578.91999999999996, 578.09000000000003,
	579.37, 580.13, 580.13999999999999, 579.50999999999999, 579.24000000000001, 
	578.65999999999997, 578.86000000000001, 578.04999999999995, 577.78999999999996,
	576.75, 576.75, 577.82000000000005, 578.63999999999999, 580.58000000000004, 
	579.48000000000002, 577.38, 576.89999999999998, 576.94000000000005, 
	576.24000000000001, 576.84000000000003, 576.85000000000002, 576.89999999999998,
	577.78999999999996, 578.17999999999995, 577.50999999999999, 577.23000000000002,
	578.41999999999996, 579.61000000000001, 579.04999999999995, 579.25999999999999,
	579.22000000000003, 579.38, 579.10000000000002, 577.95000000000005, 578.12, 579.75,
	580.85000000000002, 580.40999999999997, 579.96000000000004, 579.61000000000001,
	578.75999999999999, 578.17999999999995, 577.21000000000004, 577.13, 
	579.10000000000002, 578.25, 577.90999999999997, 576.88999999999999, 
	575.96000000000004, 576.79999999999995, 577.67999999999995, 578.38, 
	578.51999999999998, 579.74000000000001, 579.30999999999995, 579.88999999999999,
	579.96000000000004, 580.98000000000002, 581.03999999999996, 580.49000000000001,
	580.51999999999998, 578.57000000000005, 578.96000000000004, 579.94000000000005,
	579.76999999999998, 579.44000000000005, 578.97000000000003, 580.08000000000004,
	580.23000000000002, 580.75, 581.26999999999998)
, class = c("ts", "numeric")
, tsp = c(1860., 1986., 1.)
, title = "Lake Huron, mean level, July, 1860-1986"
)
mean(huron)
sd(huron)
min(huron)
max(huron)
median(huron)
boxplot(huron)
plot.ts(huron)
```
Comment:
The mean value is 579.3091.
The standard deviation value is 1.335657.
The min value is 575.96.
The max value is 581.86.
The median value is 579.44.
The boxplot shows that it does not have outliers and it seems to have a little left skewness.
The time series shows that it changes all the time.
The mean value becomes smaller as times goes, especially the mean value from 1900 to 1980 is lower than the mean valur from 1860 to 1890.
The variance becomes larger as time goes.

# (b)
```{r}
log.likelihood=function(par, x){
n=length(x)
v=x[1]^2
for (i in 2:n)
v=v+(x[i]-par[1]*x[i-1])^2
return(v/par[2]+n*log(par[2]))
}
huron2<-huron-mean(huron)
a<-nlminb(start=c(1,1),objective=log.likelihood,x=huron2,lower=c(-21,10^(-7)),upper=c(21,70))
b<-a$par[1]
b
```

# (c)
```{r}
pred.huron2=huron2
for (i in 2:length(huron2)) {
  pred.huron2[i]=b*huron2[i-1]
}
plot(huron2)
lines(pred.huron2,col=22)
```
Comment:
As we seen from the plot, at the same time (year), there is difference between true values and predicted values.
So, the true values' distribution and the predicted values' distribution are different.
However, the overall changing pattern of two distribution is nearly same.


