---
title: "Assignment 3"
author: "Wenhao Li 250959325"
date: "01/03/2020"
output: word_document
---

#Question 1
```{r}
#x,y,z
x<-seq(-pi,pi,length=50)
y<-seq(-pi,pi,length=50)
fun_xy<-function(x,y){
  (2+sin(x))*(cos(2*y))
}
z<-outer(x,y,fun_xy)

#Plot plots by three different values
persp(x,y,z,xlab="X",ylab="Y",zlab="(2+sin(x))*(cos(2*y))",main="theta=30,phi=30",theta=30,phi=30)
persp(x,y,z,xlab="X",ylab="Y",zlab="(2+sin(x))*(cos(2*y))",main="theta=60,phi=60",theta=60,phi=60)
persp(x,y,z,xlab="X",ylab="Y",zlab="(2+sin(x))*(cos(2*y))",main="theta=90,phi=90",theta=90,phi=90)
```



#Question 2
```{r}
a_fun<-function(n){
  #Error checking 
  if(!is.numeric(n)){
    stop("n should be numeric")
  }
  if(is.na(n)){
    stop("n should not indlude missing values")
  }
  #Function Body
  minimum<-sum(pmin(2^(1:n),(1:n)^3))
  maximum<-sum(pmax(2^(1:n),(1:n)^3))
  return(c(minimum,maximum))
}
```

```{r,error=TRUE}
#Test for a few bad/wrong n's
#Test for numeric
a_fun("my")
#Test for missing valus
a_fun(c(NA,30))
```

```{r}
#Execute function
sapply(seq(200,5000,by=600),a_fun)
```



#Question 3
```{r}
IQR.outliers<-function(x){
  #(a) Error Checking
  if(is.na(x)){
    stop("x should not include missing values")
  }
  if(!is.numeric(x)){
    stop("x should be numeric")
  }
  
  #(b) Compute IQR as Q3-Q1
  Q1<-quantile(x,probs = 0.25)
  Q3<-quantile(x,probs = 0.75)
  IQR<-Q3-Q1
  
  #(c) Detect suspected outlier(s)
  lowerboundary<-Q1-1.5*IQR
  upperboundary<-Q3+1.5*IQR
  outliers_lowerboundary<-x[x<lowerboundary]
  outliers_upperboundary<-x[x>upperboundary]
  
  #(d) Boxplot
  boxplot(x)
  
  #(e)Proper output
  return(list(IQR=IQR,outliers_lowerboundary=outliers_lowerboundary,outliers_upperboundary=outliers_upperboundary))
}
```


```{r,error=TRUE}
# Test with dist and speed in the data.frame cars
IQR.outliers(cars$dist)
IQR.outliers(cars$speed)

# Test with wrong inputs
IQR.outliers(c(NA,30))
```



#Question 4

# (a)
```{r}
# Import dataset
dataset1<-read.table("~/Desktop/SS2864/Assignment 3/GLB.Ts_dSST.csv",header = TRUE,sep=",")
# Keep only 13 columns
dataset2<-dataset1[,1:13]
```

# (b)
```{r}
my.newfunction<-function(x){
  # Error checking
  if(is.na(x)){
    stop("x should not include missing values")
  }
  # Function Body
  new_x<-x[-1]
  return(mean(new_x))
}
average_temperatures<-apply(dataset2,1,my.newfunction)
plot(dataset2$Year,average_temperatures,xlab="Year",ylab="Yearly Average Temperatures",main="Yearly Average Temperatures from 1880 to 2019",type="l")
```
Comment:
The overall trend of yearly average temperature from 1880 to 2019 is upward.
The yearly average temperature between 1880 and 1940 is under 0 and is stable.
The yearly average temperature increase rapidly between 1960 and 2019.


# (c)
```{r}
Years<-c(seq(1880,2000,20),2019)
n<-length(Years)
dataset3<-dataset2[Years-1880+1,2:13]
dataset4<-t(as.matrix(dataset3))
matplot(dataset4,xlab="Month",ylab="Temperature Change",type="l",col=1:n,lty=1:n)
legend("topleft",legend=Years,col=1:n,lty=1:n)
title("Monthly temperatures from Jan to Dec for some years")
```
Comment:
Each year's monthly temperatures is stable.
Monthly temperature of 2019 is much higher than other years' monthly temperature.



#Question 5
```{r}
my.ecdf<-function(x,y){
  # Error checking
  if(!is.numeric(y)){
    stop("y should be a number")
  }
  if(length(y)!=1){
    stop("y should be a vector")
  }
  # Function Body
  n<-length(x)
  a_sum<-sum(as.integer(x<=y))
  b<-a_sum/n
  return(b)
}

# Test
my.ecdf(x=rnorm(20),y=-2)
my.ecdf(x=rnorm(20),y=2)
my.ecdf(x=rnorm(20),y=median(x))

```








































